\documentclass[a4paper, 10pt]{article}
\usepackage{geometry}
\geometry{left=3cm,right=3cm,top=3cm,bottom=3cm}
\usepackage{footmisc}
\usepackage[UTF8]{ctex}
\usepackage{amsmath}
\usepackage{subfigure}
\usepackage[graphicx]{realboxes}
\setlength{\parindent}{0pt} 
\begin{document}
\title{{ \textbf {homework}\footnote{较熟的单词没有记例句，不太熟的单词记了一下例句}}}
  \author{yike}
  \date{}
  
  \maketitle

\section{day1}
1.cultivation

noun. 开垦、培养

2.infusion 

noun.灌输；注入物；激励 ex：He brought a tremendous infusion of hope to the people.

3.medieval 

adj.中世纪的、过时的 ex：medieval philosophy \& medieval music


4.ravage

verb/noun.毁坏，破坏 ex：He would never ravage flowers, certainly not in a cemetery.


5.reclamation

noun.开垦、收回、矫正 ex：agricultural reclamation  农垦

6.remuneration 

noun.酬金、薪水、赔偿 ex：arclays began a review of its remuneration policies in 2008.


7.navigation

noun.导航

8.orientation

noun.方向

9.stationary

adj.不动的，静止的，稳定的 ex：In short, the shinbashira was acting like an enormous stationary pendulum.

10.deprive 

verb.剥夺

11.evolve 

verb.进化

12.propagate

verb.散播、宣传、传播、繁殖 ex：Plants won't propagate in these conditions.

13.vulnerable 

adj.脆弱的、易碎的

14.neolithic 

adj/noun.新石器时代（的） ex：Neolithic Period/Age

15.overshadow 

verb.使黯然失色、遮盖、遮蔽 ex：Never let the outfit overshadow who you are.

16.paradox

noun.悖论

17.prohibitive

adj.禁止的

18.simultaneously 

adv.同时地

19.triumph 

noun/verb.巨大成功、重大胜利 ex：The winning team returned home in triumph.

20.evaporate

verb.蒸发、挥发、消散

\section{day2}

1.immobile

adj.不可移动的

2.cohesive 

adj.团结的

3.deviate 

verb.偏离、脱离、违背 ex：The bus had to deviate from its usual route because of a road closure.

4.entail

verb.使必要，需要；<旧>遗赠（财产），限定继承 ex：Such a decision would entail a huge political risk in the midst of the presidential campaign.

5.ostracize 

verb.放逐、排斥 ex：

6.solidarity 

noun.团结一致

7.enzyme 

noun.酶

8.navigate

verb.指引、导引、穿过、驾驶、浏览、处理


9.periodic 

adj.定期的、阶段性的

10.apparatus

noun.设备，器具；机构，组织；器官；评论性注释

11.neonate 

noun.婴儿 ex：Conclusions Premature delivery is the main causes of neonate illness and death.

12.perceptual

adj.知觉的、感知的

13.respiration 

noun.呼吸

14.stimuli 

noun.刺激物、促进因素 ex：In response to certain stimuli, many animals show instinctive aggressive reactions.

15.conflate 

verb.合并 ex：Her letters conflate past and present.

16.endorse

verb.赞同、认可、宣传 ex：I wholeheartedly endorse his remarks.


17.rational 

adj.合理的、有逻辑的

18.tactic 

noun.策略、战术/adj.按顺序排列的 ex:One tactic involves where to display the goods.

19.validate 

verb.批准,使正式有效,证实 ex:This discovery seems to validate the claims of popular astrology.

20.excavate

verb.挖掘,考古

\end{document}